### 2021-04-13 manuscript.rmd
Explaining offset, ref #1
Fix prior journal problem, ref #1
Fix table 2, ref #1

bibliography      : ["manuscript.rmd"]

@@

Comparative content analysis is a frequently used research design in journalism studies. Comparative content analysis is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI], among others. A typical comparative content analysis in journalism research includes news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Although some comparative content analysis studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles. For example, some hypotheses are "the coverage of foreign countries by the news is primarily  determined  by  geographical  proximity  and  the  status  of  the  covered  country" [@wilke:2012, p.306] and "the  degree  of  opinion-orientation  will  be  highest  in  newspapers  from  Polarized  Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g. newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g. degree of opinion-orientation), namely, the article-level.

@@

\begin{equation}
  \label{eq:2}
  z_{k} = \beta_{0} + \beta_{1} x_{k} + \epsilon_{k}
\end{equation}

@@

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. More often than not, we do not have any information to set an informative prior (e.g. What about *Journal of Communication*?). One option is to consult experts or to make an educated guess. But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].

@@

We used negative binomial regression for this analysis. Media outlets are nested in countries (e.g. *Der Standard* and *Österreichischer Rundfunk* are nested in Austria). Thus, a country-based variance is added ($\mu_{0k}$). Applying the same notation under the introduction section, the multilevel regression equations are:

\begin{align}
\log(\frac{z_{jk}}{n_{j}}) &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \epsilon_{jk}
\end{align}

@@

\begin{align}
\log(\frac{z_{jk}}{n_{j}}) &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{j}
\end{align}

@@

```{r t2, results = "asis"}
### TODO: to prim it further
require(brms)
require(parameters)
require(dplyr)
article_level <- readRDS("import_logit.RDS")
article_level %>% parameters(ci = 0.95, effects = "fixed", dispersion = TRUE, centrality = "mean", test = "pd") %>% as.data.frame -> res

res %>% dplyr::select(Parameter, Mean, SD, CI_low, CI_high) %>% rename(Estimate = Mean) %>% knitr::kable(format = "markdown", caption = "Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country", digits = 2)
```

>>>>

bibliography      : ["manuscript.bib"]

@@

Comparative content analysis is a frequently used research design in journalism studies. Comparative content analysis is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI;@grasland:2019:I], among others. A typical comparative content analysis in journalism research includes news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Although some comparative content analysis studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles. For example, some hypotheses are "the coverage of foreign countries by the news is primarily  determined  by  geographical  proximity  and  the  status  of  the  covered  country" [@wilke:2012, p.306] and "the  degree  of  opinion-orientation  will  be  highest  in  newspapers  from  Polarized  Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g. newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g. degree of opinion-orientation), namely, the article-level.

@@

\begin{equation}
  \label{eq:2}
  \log{z_{k}} = \beta_{0} + \beta_{1} x_{k} + \epsilon_{k}
\end{equation}

@@

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. More often than not, we do not have any information to set an informative prior (e.g. What about a new journal?). One option is to consult experts or to make an educated guess. But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].

@@

We used negative binomial regression for this analysis. Media outlets are nested in countries (e.g. *Der Standard* and *Österreichischer Rundfunk* are nested in Austria). Thus, a country-based variance is added ($\mu_{0k}$). We also added $\log{n_{j}}$ as an offset value. An offset value is a term that does not have the associated regression coefficient at the right-hand side of the regression equation \@ref(eq:2). Effectively, we modeled the *rate* of China coverage. Applying the same notation under the introduction section, the multilevel regression equations are:

\begin{align}
\log{z_{jk}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \log{n_j} + \epsilon_{jk} \\
\log{z_{jk}} - \log{n_j} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} +  \epsilon_{jk} \\
\log\frac{z_{jk}}{n_{j}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \epsilon_{jk} \\
\end{align}

@@

\begin{align}
\log\frac{z_{jk}}{n_{j}} &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{j}
\end{align}

@@

<!-- ```{r t2, results = "asis"} -->
<!-- ### TODO: to prim it further -->
<!-- require(brms) -->
<!-- require(parameters) -->
<!-- require(dplyr) -->
<!-- article_level <- readRDS("import_logit.RDS") -->
<!-- article_level %>% parameters(ci = 0.95, effects = "fixed", dispersion = TRUE, centrality = "mean", test = "pd") %>% as.data.frame -> res -->

<!-- res %>% dplyr::select(Parameter, Mean, SD, CI_low, CI_high) %>% rename(Estimate = Mean) %>% knitr::kable(format = "markdown", caption = "Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country", digits = 2) -->
<!-- ``` -->

Table: (\#tab:t2) Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country

| Parameter                          | Estimate | SD   | 95 \%HDI       |
|:-----------------------------------|:---------|------|----------------|
| $\gamma_{000}$ (Intercept)         | -7.06    | 0.81 | (-8.61, -5.44) |
| $\gamma_{001}$ (Log import volume) | 0.27     | 0.06 | (0.16, 0.38)   |
